Cluster Difference Imaging Photometric Survey. III. An Open Cluster Spanning 500\,Parsecs

### 2021-03-29 cluster_paper/ms.tex
update ms with phot/astrom binarity

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f3a.pdf}
			\includegraphics[width=0.49\textwidth]{f3b.pdf}
		}
	   %
		%\subfloat{
		%	\includegraphics[width=0.6\textwidth]{f3b.pdf}
		%}
	\end{center}
	\vspace{-0.7cm}
  \caption{ {\bf The core and halo of \cn\ in the space of rotation
    period and dereddened Gaia color.}
    Subset $\mathcal{A}$ ({\it top}) and $\mathcal{B}$ ({\it bottom})
    undergo successive degrees of automated cleaning, described in Section~\ref{subsubsec:cluster}.
    The Pleiades \citep[120\,Myr;][]{rebull_rotation_2016a} and
    Praesepe \citep[650\,Myr;][]{douglas_poking_2017} are shown for
    reference.
    Stars in the core and the halo of NGC\,2516 appear
    gyrochronologically coeval with the Pleiades at $(Bp-Rp)_0$$<$1.2.
    There is a narrow range of color, from $1.2<(Bp-Rp)_0<1.7$,
    in which some NGC\,2516 members appear elevated with respect to
    the Pleiades, suggesting a slightly older age.
		\label{fig:rot}
	}
\end{figure*}

@@

Figure~\ref{fig:rot} shows the resulting rotation periods, following
three different sets of cleaning criteria.  The first and second sets
of criteria were entirely automated, and yielded subsets we denote
$\mathcal{A}$ and $\mathcal{B}$.  For both subsets, we considered
light curves for which the peak Lomb-Scargle periodogram period was
below 15 days, the normalized Lomb-Scargle power exceeded 0.08, and
for which no equal-brightness or greater companions were within the
aperture.  Beyond requiring that the target star be the brightest star
in the aperture, we also required that at most one companion with
brightness exceeding one tenth of the target star's brightness be
present in the aperture according to the Gaia DR2 source catalog.  For
set $\mathcal{A}$, this yielded \nautorotnumerator light curves, out
of \nautorotdenominator stars for which rotation periods might
plausibly have been detected.  For set $\mathcal{B}$, we then
additionally required that the Lomb-Scargle and Stellingwerf
phase-dispersion methods yielded identical periods to within 10\%.
This yielded \nautorotnumeratormatching light curves.

{\bf Curtis TODO: set $\mathcal{C}$ was created through a manual
curation process.}

The comparison to the Pleiades and Praesepe is made using the rotation
periods and dereddened colors from Table~5 of
\citet{curtis_rup147_2020}, which were based data from
\citet{rebull_rotation_2016a} and \citet{douglas_k2_2019}
respectively.

A few conclusions can be drawn by comparing the \cn\ rotation periods
with those of the Pleiades and Praesepe.  The first is that in both
stages of cleaning, the core and halo of \cn\ both show
gyrochronological ``slow sequences''.  These sequences appear to be
coeval with each other, and at least to first order appear to overlap
with the Pleiades sequence.

@@

Finally, comparing the slow sequences of the Pleaides and \cn, they
appear to overlap from roughly $0.5<(Bp-Rp)_0<1.2$.  For stars that
are redder, the dispersion in rotation periods increases.  From
$1.2<(Bp-Rp)_0<1.7$, subset $\mathcal{B}$ of \cn\ has stars that
overlap with the Pleiades.  However, it also has about ten stars at
longer rotation periods---extending up to $\approx$11 days, rather
than the $\approx$8.5day limit for the Pleiades.  This is consistent
with \cn\ being slightly older than the Pleiades.

{\bf We explore this quantitatively by fitting interpolated
models}[?].  The resulting gyrochronology age we find for the core is
XXX.  For the halo, the claimed age from gyrochronology is YYY.
Applying the same procedure to the field star comparison sample (see
Appendix~\ref{app:compstar}), we get an age of ZZZ+/-AAA.

@@

\subsection{Rotation in NGC\,2516}

>>>>

\begin{figure*}[t]
	\begin{center}
		\leavevmode
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f3a.pdf}
			\includegraphics[width=0.49\textwidth]{f3b.pdf}
		}

        \vspace{-0.1cm}
		\subfloat{
			\includegraphics[width=0.49\textwidth]{f3c.pdf}
			\includegraphics[width=0.49\textwidth]{f3d.pdf}
		}
	\end{center}
	\vspace{-0.7cm}
  \caption{ {\bf TESS rotations periods and dereddened Gaia colors for \cn.}
    {\it Top row}: \cn\ split into its core and halo.  Subset
    $\mathcal{A}$ ({\it left columns}) and $\mathcal{B}$ ({\it right columns}) undergo
    successive degrees of automated cleaning, described in
    Section~\ref{subsubsec:cluster}.  The Pleiades
    \citep[120\,Myr;][]{rebull_rotation_2016a} and Praesepe
    \citep[650\,Myr;][]{douglas_poking_2017} are shown for reference.
    Stars in the core and the halo of NGC\,2516 appear
    gyrochronologically coeval with the Pleiades at $(Bp-Rp)_0$$<$1.2.
    There is a narrow range of color, from $1.2<(Bp-Rp)_0<1.7$,
    in which some NGC\,2516 members appear slightly elevated with respect to
    the Pleiades, suggesting an older age.
    {\it Bottom row}: \cn\ colored by binarity indicators.
    Sources with $\mathrm{RUWE}>1.2$ appear in red (astrometric
    binaries).
    Overplotted in orange are sources at least 0.3\,mag above an
    empirically fit cluster isochrone (photometric binaries).
		\label{fig:rot}
	}
\end{figure*}

@@

The top row of Figure~\ref{fig:rot} shows the resulting rotation
periods, following three different sets of cleaning criteria.  The
first and second sets of criteria were entirely automated, and yielded
subsets we denote $\mathcal{A}$ and $\mathcal{B}$.  For both subsets,
we considered light curves for which the peak Lomb-Scargle periodogram
period was below 15 days, the normalized Lomb-Scargle power exceeded
0.08, and for which no equal-brightness or greater companions were
within the aperture.  Beyond requiring that the target star be the
brightest star in the aperture, we also required that at most one
companion with brightness exceeding one tenth of the target star's
brightness be present in the aperture according to the Gaia DR2 source
catalog.  For set $\mathcal{A}$, this yielded \nautorotnumerator light
curves, out of \nautorotdenominator stars for which rotation periods
might plausibly have been detected.  For set $\mathcal{B}$, we 
additionally required that the Lomb-Scargle and Stellingwerf
phase-dispersion methods yielded identical periods to within 10\%.
This yielded \nautorotnumeratormatching light curves.

The comparison to the Pleiades and Praesepe is made using the rotation
periods and dereddened colors from Table~5 of
\citet{curtis_rup147_2020}, which used data from
\citet{rebull_rotation_2016a} and \citet{douglas_k2_2019}
respectively.
A few conclusions can be drawn by comparing the \cn\ rotation periods
with those of the Pleiades and Praesepe.  The first is that in both
stages of cleaning, the core and halo of \cn\ both show
gyrochronological ``slow sequences''.  These sequences appear to be
coeval with each other, and at least to first order appear to overlap
with the Pleiades sequence.

@@

Finally, comparing the slow sequences of the Pleaides and \cn, they
appear to overlap from roughly $0.5<(Bp-Rp)_0<1.2$.  For stars that
are redder, the dispersion in rotation periods increases.  From
$1.2<(Bp-Rp)_0<1.7$, subset $\mathcal{B}$ of \cn\ has stars that
overlap with the Pleiades.  However, it also has about ten stars at
longer rotation periods---extending up to $\approx$11 days, rather
than the $\approx$8.5day limit for the Pleiades.  This is consistent
with \cn\ being slightly older than the Pleiades.
{\bf We explore this quantitatively by fitting interpolated
models}[?].  The resulting gyrochronology age we find for the core is
XXX.  For the halo, the claimed age from gyrochronology is YYY.
Applying the same procedure to the field star comparison sample (see
Appendix~\ref{app:compstar}), we get an age of ZZZ+/-AAA.

The bottom row of Figure~\ref{fig:rot} shows the same data, with the
points colored by indicators of binarity.
To assess astrometric binarity, we used the renormalized unit weight
error (RUWE) from Gaia EDR3.
For plotting purposes, we labeled anything with RUWE exceeding 1.2 as
an astrometric binary (11\% of the overall cluster
sample).
A cautionary point is that poor astrometric fits can also be caused by
photometric variability.
To assess photometric binarity, we fitted a spline to
Figure~\ref{fig:hr} by hand, and labelled any points brighter than
0.3\,mag above the cluster sequence as photometric binaries.
This included 20\% of the overall cluster sample.
Many of the resulting candidate binaries, though not all of them,
appear underneath the ``slow sequence''.
We speculate on possible explanations in Section~\ref{disc:rotn}.

@@

\subsection{Rotation in NGC\,2516}
\label{disc:rotn}
